Dynamics of thin liquid film flows studied with the lattice Boltzmann method

### 2022-12-22 others/prolog.tex
Updates from Overleaf

\section*{Prolog}
\label{sec:prolog}
My time as a student hopefully and finally ends with this work, my thesis.
I started studying physics quite some time ago and honestly doing research for my doctorate feels very different from what university was before.
While there are many things to write here as objective as possible, most of it is tainted with my style.
Therefore I want to use this prologue as a short but to me important personal summary.
Working on problems nobody has solved or thought about is hard.
Creativity is an essential skill to perform research.
Often it is easy to do the same over and over again, most of the time following orders is also easy.
Finding my very own way to approach problems and designing computational experiments was unbelievable hard work. 
Not only did I do far more things wrong than right, but I also had a naive and idealistic view of science.
But science is done by humans.
Doing research can be fairly disappointing on the one hand but also very rewarding on the other.
For me it was mostly the former and while failures or null results are an integral part of science they are rarely communicated.
A situation which at least from my point of view does not improve the quality of research and in fact does inevitably lead to recurring mistakes and thus wasted effort.
It is well known that most of academia's staff is showing symptoms of burnout and are exposed to constant elevated levels of stress~\cite{gewin2021pandemic, bilge2006examining, henny2014prevalence, watts2011burnout, satinsky2021systematic}.
I am just a PhD student, but even I felt guilty during weekends for not working and instead engaged in leisure activities.
Why did I feel guilty, because projects did not work the way they should have and results did not agree with hypotheses.
That put pressure on me, because whatever we do we want to see progress.
If nothing adds up and you hit a dead end after another it is hard to see progress.

>>>>

\section*{Prolog}
\label{sec:prolog}
My time as a student hopefully and finally ends with this work, my thesis.
I started studying physics quite some time ago and honestly doing research for my doctorate feels very different from what university was before.
While there are many things to write here as objective as possible, most of it is tainted with my style.
Therefore I want to use this prologue as a short but to me important personal summary.
Working on problems nobody has solved or thought about is hard.
Creativity is an essential skill to perform research.
Often it is easy to do the same over and over again, most of the time following orders is also easy.
Finding my very own way to approach problems and designing computational experiments was unbelievable hard work. 
Not only did I do far more things wrong than right, but I also had a naive and idealistic view of science.
But science is done by humans.
Doing research can be fairly disappointing on the one hand but also very rewarding on the other.
For me it was mostly the former and while failures or null results are an integral part of science they are rarely communicated.
A situation which at least from my point of view does not improve the quality of research and in fact does inevitably lead to recurring mistakes and thus wasted effort.
It is well known that most of academia's staff is showing symptoms of burnout and are exposed to constant elevated levels of stress~\cite{gewinPandemicBurnoutRampant2021, bilgeExaminingBurnoutAcademics2006, wattsBurnoutUniversityTeaching2011, satinskySystematicReviewMetaanalysis2021}.
I am just a PhD student, but even I felt guilty during weekends for not working and instead engaged in leisure activities.
Why did I feel guilty, because projects did not work the way they should have and results did not agree with hypotheses.
That put pressure on me, because whatever we do we want to see progress.
If nothing adds up and you hit a dead end after another it is hard to see progress.
